Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-21 thirdPaper/draft/typeConeAssociahedra.tex
Minor changes and comments to Section 4.

\begin{theorem}
\label{theo::brick-algebra-condition}
 Let~$\Lambda$ be an Artin algebra all of whose non-injective indecomposable objects are bricks and all of whose indecomposable objects are~$\tau$-rigid\yann{Are there examples of representation-infinite algebras which satisfy those assumptions?}. Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any non-projective indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
\end{theorem}

@@

\begin{lemma}
\label{lemm::then-AR-seq-are-mutation}
Let~$\Lambda$ be an Artin algebra, let~$\tau X\infl E\defl X$ be an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$ and denote~$FX=M$.
Assume that:\yann{There might be some redundancies in the assumptions}
\begin{enumerate}
 \item $X\notin\add(\susp\Lambda)$;
 \item $M$ and~$\tau M$ are~$\tau$-rigid;
 \item $\Hom{\Lambda}(M,\tau^2 M)=0$;
 \item $\tau M$ is a brick.
\end{enumerate}
Then~$\tau X\infl E\defl X$ is a mutation conflation.
\end{lemma}

@@

\begin{proof}
In this proof, we implicitely identify the projective indecomposable~$\Lambda$-module~$P$ with the complex~$P$ concentrated in degree~$0$.

@@

(0) Since~$P$ is concentrated in only one degree, it is rigid in~~$K^{[-1,0]}(\proj\Lambda)$ and so is~$\susp P$.
Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.

@@

(5) $\Hom{K^b}(\susp P,\susp E)= 0$:
Let~$P\xrightarrow{f} E$ be any morphism.
Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
By the previous lemma, or by (4), the morphism~$g$ factors through~$\alpha$: there is some~$h$ such that~$g= h \alpha$.

>>>>

\begin{theorem}
\label{theo::brick-algebra-condition}
 Let~$\Lambda$ be an Artin algebra all of whose non-injective indecomposable objects are bricks and all of whose indecomposable objects are~$\tau$-rigid\yann{Are there examples of representation-infinite algebras which satisfy those assumptions?}. Then the almost-split conflations of~$K^{[-1,0]}(\proj \Lambda)$ are mutation conflations if and only if for any non-projective indecomposable~$\Lambda$-module~$M$, the space~$\Hom{\Lambda}(M, \tau^2 M)$ vanishes.
\end{theorem}
\pg{Should define mutation conflations}

@@

\begin{lemma}
\label{lemm::then-AR-seq-are-mutation}
Let~$\Lambda$ be an Artin algebra, let~$\tau X\infl E\defl X$ be an Auslander--Reiten conflation in~$K^{[-1,0]}(\proj\Lambda)$ and denote~$FX=M$.
Assume that:\yann{There might be some redundancies in the assumptions}\pg{If so, it's not obvious to me.}
\begin{enumerate}
 \item $X\notin\add(\susp\Lambda)$;
 \item $M$ and~$\tau M$ are~$\tau$-rigid;
 \item $\Hom{\Lambda}(M,\tau^2 M)=0$;
 \item $\tau M$ is a brick.
\end{enumerate}
Then~$\tau X\infl E\defl X$ is a mutation conflation.
\end{lemma}

@@

\begin{proof}
In this proof, we implicitly identify the projective indecomposable~$\Lambda$-module~$P$ with the complex~$P$ concentrated in degree~$0$.

@@

(0) Since~$P$ is concentrated in only one degree, it is rigid in~~$K^{[-1,0]}(\proj\Lambda)$ and so is~$\susp P$.
Moreover,~$FY=I$ is~$\tau$-rigid, hence~$Y$ is rigid in~$K^{[-1,0]}(\proj\Lambda)$ by~\cite[Lemma 3.4]{AdachiIyamaReiten}.\pg{Injectives are not necessarily tau-rigid. Need that Lambda is a brick algebra?}

@@

(5) $\Hom{K^b}(\susp P,\susp E)= 0$:
Let~$P\xrightarrow{f} E$ be any morphism.
Since~$P$ is rigid,~$f$ factors through the inflation~$\beta$ in the conflation~$Y\infl E\defl \susp P$, and there is some morphism~$g$ such that~$f=\beta g$.
By the previous lemma, or by (4), the morphism~$g$ factors through~$\alpha$: there is some~$h$ such that~$g= h \alpha$.\pg{What is alpha?}
